---
title: "TxRegQuery"
author: "Shweta Gopaulakrishnan, reshg at channing.harvard.edu, BJ Stubbs rebjh at channing.harvard.edu"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: pdf_document
vignette: >
  %\VignetteIndexEntry{TxRegQuery}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# Introduction

TxRegQuery is an R package that utilizes mongolite, GenomicRanges, and bigrquery to provide users with specialized tools for information access, retrieval from both MongoDB/Drill and BigQuery backends. TxRegQuery makes it possible to extract data in the form of GRanges objects, which can be filtered and intersected to create node-edge lists used in the formulation of regulatory networks. 

Our database "txregnet" hosts the following types of data : 

1.  eQTL/GWAS data
- GTEx eqtl files: /udd/reala/repos/analyses/TxRegNet/data/eQTL/GTEx_v6p/filtered_0.05/eqtl_files

2.  Annotations

- Encode DNAse hypersensitivity bed files: /proj/rerefs/reref00/ENCODE/DNaseI_Roadmap_Encode/BEDFILES
- Roadmap digital genomic footprints: /udd/reala/reference_files/annotations/ROADMAP_DGF/

The Transcription factor data is currently on shion. 

3. TF data

- Kimbie's CISBP FIMO scan TF bed files: /udd/rekrg/EpiPANDA/FIMO_results/ScanBedResults - http://cisbp.ccbr.utoronto.ca/faq.html is origin of PSSM

- Kheradpour TF sites are located at: /udd/reala/reference_files/eqtl_gwas/matches.txt.gz

```{r setup, include=FALSE}
suppressPackageStartupMessages({
library(TxRegQuery)
library(mongolite)
library(RMongo)
library(GenomicRanges)
})
```
# MongoDB as a backend 

Structure : 
We have a mongo database "txregnet" hosting multiple collections for the eQTL, FootPrint, DNASe HyperSensitivity data. 
## Establish connection 
 
To successfully connect to our "txregnet" database and view the collections present :  

```{r dobanoyy}
conn = mongoSource()

```
To access the different collections : 

## eQTL
### To retrieve GRanges of the eQTL's : 

```{r eqtl}

myoff=100*1000
mystartGo=38077296-myoff
myendGo=38083884+myoff
mychrGo=17
mycollGo="Cells_Transformed_fibroblasts_Analysis_v6p_all_snpgene_pairs_eQTL"
mydbGo="txregnet"
res_eqtl=getMongoRangeEqtl(mychrGo,mystartGo,myendGo,mycollGo,mydbGo)
res_eqtl
```

## Annotation Data
### To retrieve the GRanges of Footprints data :

```{r footprint}

myoff=100*1000
mystartGo=38077296-myoff
myendGo=38083884+myoff
mychrGo="chr17"
mydbGo="txregnet"
mycollGo="CD19_DS17186_hg19_FP"
res_fp=getMongoRangeFp(mychrGo,mystartGo,myendGo,mycollGo,mydbGo)
res_fp
```

# Apache Drill
## Transcription Factor Data

We use Apache Drill to extract the GRanges of the Transcription Factor data present on (shion currently)

# BigQuery as a backend

Structure:

We have defined a dataset "txregnet" under the project "cgc-xx-xxx". There are three tables "eQTL", "FP", "TF". 
It is required to have a billing group set up with BigQuery.

To access the data on BigQuery : 

## eQTL 
### To retrieve the GRanges of the eQTL's : 

```{r bigeqtl}

mychrGo="17"
mystartGo=41196312-500*1000
myendGo=41322262+500*1000
myprojectGo="cgc-xx-xxxx"
mydatasetGo="txregnet"
mybillingGo = "cgc-xx-xxxx"
res_eqtl=getBigqueryRangeEqtl(mychrGo,mystartGo,myendGo,myprojectGo,mydatasetGo,mybillingGo)
res_eqtl
```
## Annotation Data 
### To retrieve the GRanges of Footprint's data : 

```{r bigfp}

mychrGo="chr17"
mystartGo=41196312-500*1000
myendGo=41322262+500*1000
myprojectGo="cgc-xx-xxxx"
mydatasetGo="txregnet"
mybillingGo = "cgc-xx-xxxx"
res_fp=getBigqueryRangeFp(mychrGo,mystartGo,myendGo,myprojectGo,mydatasetGo,mybillingGo)
res_fp
```
## Transcription Factor Data
### To retrieve the GRanges of the TF data : 

```{r tf}

mychrGo="chr17"
mystartGo=41196312-500*1000
myendGo=41322262+500*1000
myprojectGo="cgc-xx-xxxx"
mydatasetGo="txregnet"
mybillingGo = "cgc-xx-xxxx"
res_tf=getBigqueryRangeTf(mychrGo,mystartGo,myendGo,myprojectGo,mydatasetGo,mybillingGo)
res_tf
```
# neo4j Building 



